### 2014-11-12 nqueens.tex
Fixed typos.
english and some extra info

The CLM solution considers the chess board as a graph where nodes exchange valid
configurations between each other. First, we start with the empty
state in the first row of the chess board. Then, each square adds its own
position to the state and sends the state down, to the next row. Once a square
receives new configurations, it attempts to add its position to the
configurations. If valid, that configuration is then sent, recursively, to the
next row, until all rows are traversed. At the end of the program, the nodes at
the bottom row will have all the valid configurations.

Since computation goes from the top row to the bottom row, not all placements of
nodes on threads may be equally performant. This is especially true because the
bottom rows tend to perform the most work. The best placement is then to split the
board vertically, so that, in optimal conditions, each thread gets the same
number of columns. Our experiments show that, on shared memory, it does not
matter much if we start with a bad placement since node stealing overcomes those
issues by improving load balancing dynamically. However, we noticed interesting
cache effects when prioritizing nodes in bottom rows. The N Queens program
builds and shares lists representing valid board states and needs to iterate
over those lists often when checking if a new position does not invalidate a state.
We thus used coordination axioms \texttt{set-default-priority(A, X)} and \texttt{set-cpu(A,
vertical(X, Y))}, where \texttt{X} is the row number (0 is the top row) and
\texttt{Y} is the column number.

Experimenta results are presented in Fig.~\ref{results:nqueens}.
We first ran the coordinated program using dynamic partitioning (with work
stealing) and saw some performance improvements (\textbf{Coordinated}). However, using dynamic
partitioning is bad for memory locality since threads will steal nodes often.
We then added \texttt{set-static(A)} as a coordination axiom and saw
performance improvement (\textbf{Static}), especially when the board columns are perfectly
partitioned by the number of threads (in our case 13 threads).

>>>>

The CLM solution considers the squares of the chess board as a graph
of nodes which exchange valid configurations with each
other. Initially every square in the first row of the board gets the
empty state.  Then, each square adds its own position to the state and
sends the state down, to the next row. Once a square receives new
configurations, it attempts to add its position to the
configurations. If valid, that configuration is then sent,
recursively, to the next row, until all rows are traversed. At the end
of the program, the squares at the bottom row will have all the valid
configurations.

Since computation goes from the top row to the bottom row, not all
placements of nodes to threads performane equally. This is especially
true because the bottom rows tend to perform the most work. The best
placement is then to split the board vertically so each thread gets
the same number of columns. Our experiments show that, on a shared
memory system, it does not matter much if we start with a bad
placement since node stealing overcomes those issues by load balancing
dynamically. However, we noticed interesting cache effects when
prioritizing nodes in bottom rows.\snote{Expand on this?  What are
they?} The N Queens program builds and shares lists representing valid
board states and needs to iterate over those lists often when checking
if a new position does not invalidate a state.  We thus used
coordination axioms \texttt{set-default-priority(A, X)}
and \texttt{set-cpu(A, vertical(X, Y))}, where \texttt{X} is the row
number (0 is the top row) \texttt{Y} is the column number to
prioritize the evaluation of squares at the XXXX of the board and to
keep board configurations in the same cache. \snote{check the previous}

Experimental results are presented in Fig.~\ref{results:nqueens}.  We
first ran the coordinated program using dynamic partitioning (with
work stealing) and saw some performance improvements
(\textbf{Coordinated}). However, using dynamic partitioning is bad for
memory locality since threads will often steal nodes.  We then
added \texttt{set-static(A)} as a coordination axiom and saw
performance improvement (\textbf{Static}), especially when the board
columns are perfectly partitioned by the number of threads (in our
case 13 threads).
